### 2017-12-05 master/paper.tex
Add master for master's thesis

\documentclass[JIP]{ipsj_v2/UTF8/ipsj}

@@

\def\Underline{\setbox0\hbox\bgroup\let\\\endUnderline}
\def\endUnderline{\vphantom{y}\egroup\smash{\underline{\box0}}\\}
\def\|{\verb|}

\setcounter{volume}{22}% vol22=2014
\setcounter{number}{4}% 1=Jan., 2=Apr., 3=July, 4=Oct.
\setcounter{page}{1}

\received{2014}{3}{4}
%\rereceived{2011}{10}{1}   % optional
%\rerereceived{2011}{10}{31} % optional
\accepted{2014}{8}{1}

\usepackage[varg]{txfonts}%%!!
\makeatletter%
\input{ot1txtt.fd}
\makeatother%

@@

\title{Component-Based mruby Platform for IoT Devices}

\affiliate{OSAKA}{Graduate School of Engineering Science, Osaka University}
\affiliate{NAGOYA}{Graduate School of Informatics, Nagoya University}
\affiliate{OKUMA}{OKUMA Corporation}

\author{Takuro Yamamoto}{OSAKA}
\author{Takuma Hara}{NAGOYA}
\author{Takuya Ishikawa}{NAGOYA}
\author{Hiroshi Oyama}{OKUMA}
\author{Hiroaki Takada}{NAGOYA}
\author{Takuya Azumi}{OSAKA}

@@

\begin{keyword}
Internet of Things, software development framework, component-based development, embedded systems
\end{keyword}

\maketitle

%1
\vspace{-1mm}
\section{Introduction}
\label{sec:Introduction}
\vspace{-1mm}

@@

{\bf Organization}: The remainder of this paper is organized as follows.
Section \ref{sec:System Model} introduces the system model and the basic technologies, i.e., TECS, mruby, and mruby on TECS.
Section \ref{sec:Proposed Framework} describes the design and implementation of the proposed framework, including TINET+TECS and TLSF+TECS.
Section \ref{sec:Evaluation} evaluates the proposed framework.
Related work is discussed in Section \ref{sec:Related Work} and Section \ref{sec:Conclusion} concludes this paper.

%2
\vspace{-1mm}
\section{System Model}
\label{sec:System Model}
\vspace{-1mm}

This section describes the system model of the proposed framework, including basic technologies such as TECS and mruby.
The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}\cite{par:mrubyonTECS3}, and utilizes two technologies: mruby and TECS.
The system model of the proposed framework is shown in Fig.\ref{fig:SystemModel}.
In the proposed framework, each mruby program runs on a RiteVM mapped to a componentized task of an RTOS.
mruby programs can call the TINET functions required for network programming through the mruby-TECS bridge, and thus software to be embedded in IoT devices can be developed.
Moreover, the proposed framework comprises TLSF+TECS.
TLSF+TECS is utilized for memory management of mruby's RiteVMs and TINET+TECS, which helps to improve the efficiency of memory consumption.
The following subsection explains TECS, mruby, and mruby on TECS framework.

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/SystemModel.pdf}
    \vspace{-1mm} \caption{System model of the proposed framework}
    \vspace{-2mm} \label{fig:SystemModel}
\end{figure}

\vspace{-3mm}
\subsection{TECS}
\label{sec:TECS}
\vspace{-1mm}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/component_diagram.pdf}
    \vspace{-1mm} \caption{Component Diagram}
    \vspace{-2mm} \label{fig:component}
\end{figure}

\subsubsection{Component Model}
Fig.\ref{fig:component} shows a component diagram.
A {\it cell}, which is an instance of a TECS component, consists of {\it entry} ports, {\it call} ports, attributes and variables.
An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
A {\it cell} has one or more {\it entry} ports and {\it call} ports.
{\it Cell} functions are implemented in C.

@@

\subsubsection{Component Description}
In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
These components are described as follows.

\begin{description}
    \item[{\bf Signature Description}]
        The {\it signature} defines a {\it cell} interface.
        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Fig.\ref{signature}).
        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
signature sMotor {
    void initializePort( [in]int32_t type );
    ER setPower( [in]int power );
    ER stop( [in] bool_t brake );
};
\end{lstlisting}
\vspace{-2mm} \caption{Signature Description}
\vspace{-2mm} \label{signature}
\end{figure}
    \item[{\bf Celltype Description}]
        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Fig.\ref{celltype}).
        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
        {\it Call} ports are defined similarly.
        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tCaller {
    call sMotor cMotor;
};
celltype tMotor {
    entry sMotor eMotor;
    attr { int32_t port; };
    var { int32_t currentSpeed = 0; };
};
\end{lstlisting}
\vspace{-2mm} \caption{Celltype Description}
\vspace{-2mm} \label{celltype}
\end{figure}
    \item[{\bf Build Description}]
        The build description is used to instantiate and connect {\it cell}s.
        Fig.\ref{build} shows an example of a build description.
        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
        In Fig.\ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
        {\it C\_EXP} calls macros defined in C files.

\begin{figure}[t]
\centering
\begin{lstlisting}
cell tMotor Motor {
    port = C_EXP("PORT_A");
};
cell tCaller Caller {
    cMotor = Motor.eMotor;
};
\end{lstlisting}
\vspace{-2mm} \caption{Build Description}
\vspace{-2mm} \label{build}
\end{figure}

@@

\subsubsection{Development Flow}

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/TECSFlow.pdf}
    \vspace{-1mm} \caption{Development flow using TECS}
    \vspace{-2mm} \label{fig:TECSFlow}
\end{figure}

@@

\vspace{-3mm}
\subsection{mruby}
\label{sec:mruby}
\vspace{-1mm}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mruby.pdf}
    \vspace{-1mm} \caption{mruby/RiteVM mechanism}
    \vspace{-2mm} \label{fig:mruby}
\end{figure}

\vspace{-3mm}
\subsection{mruby on TECS}
\label{sec:mrubyonTECS}
\vspace{-1mm}

@@

\subsubsection{System Model of mruby on TECS}
% The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyonTECS}.
Each mruby program, which is a bytecode, runs on own RiteVM as a componentized task of an RTOS.
TECS components support various embedded drivers such as motor and sensor drivers.
An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.

@@

\subsubsection{mruby-TECS Bridge}
There is a significant difference between the execution times of mruby and C language codes.
According to  \cite{par:mrubyonTECS}, mruby programs are several hundred times slower than C programs and the execution of an mruby bytecode on a RiteVM is not as efficient as that of C code.
Thus, it is difficult to use mruby exclusively.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mrubyTECSbridge.pdf}
\vspace{-1mm} \caption{mruby-TECS bridge}
\vspace{-2mm} \label{fig:mrubyTECSbridge}
\end{figure}

@@

%3
\vspace{-1mm}
\section{Proposed Framework}
\label{sec:Proposed Framework}
\vspace{-1mm}

@@

\vspace{-3mm}
\subsection{TINET+TECS}
\label{sec:TINET+TECS}
\vspace{-1mm}

\subsubsection{TINET}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/TINETHierarchyDiagram.pdf}
    \vspace{-1mm} \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
    \vspace{-2mm} \label{fig:TINETHierarchyDiagram}
\end{figure}

\subsubsection{Component Design of TINET+TECS}

@@

\subsubsection*{Components of a protocol stack}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/ComponentProtocolStack.pdf}
    \vspace{-1mm} \caption{Component diagram of a protocol stack}
    \vspace{-2mm} \label{fig:ComponentProtocolStack}
\end{figure}

@@

\subsubsection*{Memory allocator component}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/tMemoryAllocator.pdf}
    \vspace{-1mm} \caption{Component diagram of tMemoryAllocator}
    \vspace{-2mm} \label{fig:tMemoryAllocator}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/SendReceive.pdf}
    \vspace{-1mm} \caption{Differences between in/out and send/receive}
    \vspace{-2mm} \label{fig:SendReceive}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sNicDriver {
  void start(
    [send(sNetworkAlloc),size_is(size)]
        int8_t *outputp, .., ..);
  void read(
    [receive(sNetworkAlloc),size_is(*size)]
        int8_t **inputp, .., ..);
    /* Omit: other functions */
};
\end{lstlisting}
\vspace{-1mm} \caption{Signature description of the nic driver (An example of send/receive)}
\vspace{-2mm} \label{src:SendReceive}
\end{figure}

\subsubsection{Dynamic connection in TECS}
\label{sec:DynamicConnection}

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/DynamicConnection.pdf}
    \vspace{-1mm} \caption{Dynamic connection}
    \vspace{-2mm} \label{fig:DynamicConnection}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
    \vspace{-1mm} \caption{Dynamic connection between CEP and REP}
    \vspace{-2mm} \label{fig:DynamicConnectionUseCase}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sRepSelector {
    void  getRep([out]Descriptor(sREP4) *desc,
                 [in]int_t i);
};
celltype tRepSelector {
    entry sRepSelector eRepSelector;
    [ref_desc]
        call sREP4 cREP[NUM_REP];
};
celltype tTCPCEP {
    call sRepSelector cRepSelector;
    [dynamic]
        call sREP4 cREP;
    /* Omit: other call/entry ports */
    /* Omit: attributes and variables */
};
\end{lstlisting}
\vspace{-1mm} \caption{Signature and celltype description for the dynamic connection}
\vspace{-2mm} \label{src:DynamicCDLcode}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
eAPI_accept (.., ..) {
    /* Get a descriptor of intended REP cell */
    cRepSelector_getRep(&desc, repid);
    /* Set the descriptor */
    cREP_set_descriptor(desc);
    /* Call the function of intended REP cell */
    cREP_getEndpoint();
}
\end{lstlisting}
\vspace{-1mm} \caption{Accept function (a dynamic connection example)}
\vspace{-2mm} \label{src:DynamicCcode}
\end{figure}

\vspace{-3mm}
\subsection{TLSF+TECS}
\label{sec:TLSF+TECS}
\vspace{-1mm}

\subsubsection{TLSF}

@@

\subsubsection{TLSF Algorithms}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/TLSF.pdf}
    \vspace{-1mm} \caption{TLSF Algorithm}
    \vspace{-2mm} \label{fig:TLSF}
\end{figure}

\subsubsection{Component Design of TLSF+TECS}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sMalloc {
  int    initializeMemoryPool(void);
  void   *calloc([in]size_t nelem,[in]size_t size);
  void   *malloc([in]size_t size);
  void   *realloc([in]const void *ptr,[in]size_t size);
  void   free([in]const void *ptr);
};
\end{lstlisting}
\vspace{-1mm} \caption{Signature description of memory management}  
\vspace{-2mm} \label{src:TLSFSignature}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tTLSFMalloc {
    [inline]entry  sMalloc  eMalloc;
    attr {
        size_t  memoryPoolSize;
    };
    var {
        [size_is(memoryPoolSize/8)]uint64_t *pool;
    };
};
\end{lstlisting}
\vspace{-1mm} \caption{Celltype description of TLSF memory allocator component}  
\vspace{-2mm} \label{src:TLSFCelltype}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/WithoutTECS.pdf}
    \vspace{-1mm} \caption{TLSF before componentization}
    \vspace{-2mm} \label{fig:WithoutTECS}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/WithTECS.pdf}
    \vspace{-1mm} \caption{TLSF after componentization}
    \vspace{-2mm} \label{fig:WithTECS}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
cell tTask Task_001 {
    cMalloc = TLSFMalloc_001.eMalloc;
};
cell tTLSFMalloc TLSFMalloc_001 {
    memoryPoolSize = 1024*1024; /* 1MB */
};
cell tTask Task_002 {
    cMalloc = TLSFMalloc_002.eMalloc;
};
cell tTLSFMalloc TLSFMalloc_002 {
    memoryPoolSize = 2*1024*1024; /* 2MB */
};
\end{lstlisting}
\vspace{-1mm} \caption{Build description of TLSF memory allocator component}
\vspace{-2mm} \label{src:TLSFBuild}
\end{figure}

\begin{figure}[t]
\centering
\begin{lstlisting}
void*
mrb_TECS_allocf(mrb_state *mrb, void *p, 
                  size_t size, void *ud)
{
    CELLCB	*p_cellcb = (CELLCB *)ud;
    if (size == 0) {
        //tlsf_free(p);
        cMalloc_free(p);
        return NULL;
    }
    else if (p) {
        //return tlsf_realloc(p, size);
        return cMalloc_realloc(p, size);
    }
    else {
        //return tlsf_malloc(size);
        return cMalloc_malloc(size);
    }
}
\end{lstlisting}
\vspace{-1mm} \caption{Example of TLSF memory allocator component}  
\vspace{-2mm} \label{src:TLSFC}
\end{figure}

@@

\subsubsection*{Multiple RiteVM}

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/UseCase_mruby.pdf}
    \vspace{-1mm} \caption{Component description of RiteVM and TLSF+TECS}
    \vspace{-2mm} \label{fig:UseCase_mruby}
\end{figure}

@@

\subsubsection*{Memory management for data sending and receiving}

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/UseCase_TINET.pdf}
    \vspace{-1mm} \caption{Fixed-size and TLSF memory allocator components}
    \vspace{-2mm} \label{fig:UseCase_TINET}
\end{figure}

@@

\vspace{-3mm}
\subsection{Use case}
\label{sec:UseCase}
\vspace{-1mm}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}[language=Ruby]
begin
    io = AnalogIO.new(A0, INPUT)
    cep = TCP.new()	
    cep.accept
    loop do		
        val = io.read  
        cep.snd val.to_s + "\n"		
        RTOS.delay(1000)			
    end
rescue => e	
    puts "[ERROR]" + e
end
\end{lstlisting}
\vspace{-1mm} \caption{Example of mruby application}
\vspace{-2mm} \label{src:mruby}
\end{figure}

\vspace{-1mm}
\section{Evaluation}
\label{sec:Evaluation}
\vspace{-1mm}

This section describes the experimental evaluation used to demonstrate the effectiveness of the proposed framework.
GR-PEACH was employed as the evaluation board.
Detailed specifications of the board are shown in Table \ref{tab:EvaluationBoardEnvironment}.
We also employ TINET 1.5.4 and the compiler arm-none-eabi-gcc 5.2
To pretest the system, we connected the board to a host PC via a LAN cable and evaluated the data sending and receiving.

\begin{table}[t]
    \centering
    \vspace{-1mm} \caption{Evaluation Board Environment}
    \begin{tabular}{l|l}
        \hline\hline
        Board           &   GR-PEACH                \\
        CPU             &   Cortex-A9 RZ/A1H 400MHz \\
        Flash ROM       &   8 MB                    \\
        RAM             &   10 MB                   \\
        LAN Controller  &   LAN8710A                \\
        \hline
    \end{tabular}
    \vspace{-2mm}
    \label{tab:EvaluationBoardEnvironment}
\end{table}

\vspace{-3mm}
\subsection{Performance of TINET+TECS}
\vspace{-1mm}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/EvaluationOfExecutionTime.pdf}
    \vspace{-1mm} \caption{Execution times of TINET and TINET+TECS}
    \vspace{-2mm} \label{fig:EvaluationOfExecutionTime}
\end{figure}

@@

%5
\vspace{-1mm}
\section{Related Work}
\label{sec:Related Work}
\vspace{-1mm}

@@

%6
\vspace{-1mm}
\section{Conclusion}
\label{sec:Conclusion}
\vspace{-1mm}

>>>>

% Master Thesis
% For Japanese
% \documentclass[a4j,12pt,oneside,openany]{jsbook}
% For English
\documentclass[a4j,12pt,oneside,openany,english]{jsbook}

@@

% jsbook to report
\usepackage{styles/utf8/book2report}

% For Theorem, Definition, Example, Proof etc.
\usepackage{styles/utf8/thesis}

% Title Font
\renewcommand{\headfont}{\bfseries}

% If the number of pages is small
\renewcommand{\baselinestretch}{1.1}

@@

% Title
\thispagestyle{empty}
\begin{center}
\vspace*{5mm}
{\Huge {\bf Master's Thesis}}\\
\vspace{2cm}
% {\Large 題\hspace{8mm}目}\\
% \vspace{1cm}
\underline{\LARGE{Component-Based mruby Platform for IoT Devices}} \\
% \vspace{0.5cm}
% \underline{\LARGE{My Bachelor Thesis}} \\
\vspace{12mm}
{\large Supervisor}\\
\vspace{6mm}
\underline{\Large Professor Toshimitsu Ushio}\\
　\\
\underline{\Large Assistant Professor Takuya Azumi}\\
\vspace{8mm}
{\large By}\\
\vspace{6mm}
\underline{\Large Takuro Yamamoto}\\
\vspace{10mm}
{\Large February 7, 2018}\\
\vspace{14mm}
{\Large Division of Mathematical Science for Social Systems,\\Department of Systems Innovation,\\Graduate School of Engineering Science, Osaka University}\\
\end{center}
\clearpage
\setcounter{page}{0}
\pagenumbering{roman}

@@

% Contens
\clearpage
\tableofcontents
\clearpage
\setcounter{page}{0}
\pagenumbering{arabic}

%1
\chapter{Introduction}
\label{sec:Introduction}

@@

{\bf Organization}: The remainder of this paper is organized as follows.
Chapter \ref{sec:System Model} introduces the system model and the basic technologies, i.e., TECS, mruby, and mruby on TECS.
Chapter \ref{sec:Proposed Framework} describes the design and implementation of the proposed framework, including TINET+TECS and TLSF+TECS.
Chapter \ref{sec:Evaluation} evaluates the proposed framework.
Related work is discussed in Chapter \ref{sec:Related Work} and Chapter \ref{sec:Conclusion} concludes this paper.

%2
\chapter{System Model}
\label{sec:System Model}

This chapter describes the system model of the proposed framework, including basic technologies such as TECS and mruby.
The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}\cite{par:mrubyonTECS3}, and utilizes two technologies: mruby and TECS.
The system model of the proposed framework is shown in Fig.\ref{fig:SystemModel}.
In the proposed framework, each mruby program runs on a RiteVM mapped to a componentized task of an RTOS.
mruby programs can call the TINET functions required for network programming through the mruby-TECS bridge, and thus software to be embedded in IoT devices can be developed.
Moreover, the proposed framework comprises TLSF+TECS.
TLSF+TECS is utilized for memory management of mruby's RiteVMs and TINET+TECS, which helps to improve the efficiency of memory consumption.
The following section explains TECS, mruby, and mruby on TECS framework.

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/SystemModel.pdf}
    \caption{System model of the proposed framework}
    \label{fig:SystemModel}
\end{figure}

\section{TECS}
\label{sec:TECS}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/component_diagram.pdf}
    \caption{Component Diagram}
    \label{fig:component}
\end{figure}

\subsection{Component Model}
Fig.\ref{fig:component} shows a component diagram.
A {\it cell}, which is an instance of a TECS component, consists of {\it entry} ports, {\it call} ports, attributes and variables.
An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
A {\it cell} has one or more {\it entry} ports and {\it call} ports.
{\it Cell} functions are implemented in C.

@@

\subsection{Component Description}
In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
These components are described as follows.

\begin{description}
    \item[{\bf Signature Description}]
        The {\it signature} defines a {\it cell} interface.
        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Fig.\ref{signature}).
        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
signature sMotor {
    void initializePort( [in]int32_t type );
    ER setPower( [in]int power );
    ER stop( [in] bool_t brake );
};
\end{lstlisting}
\caption{Signature Description}
\label{signature}
\end{figure}
    \item[{\bf Celltype Description}]
        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Fig.\ref{celltype}).
        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
        {\it Call} ports are defined similarly.
        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tCaller {
    call sMotor cMotor;
};
celltype tMotor {
    entry sMotor eMotor;
    attr { int32_t port; };
    var { int32_t currentSpeed = 0; };
};
\end{lstlisting}
\caption{Celltype Description}
\label{celltype}
\end{figure}
    \item[{\bf Build Description}]
        The build description is used to instantiate and connect {\it cell}s.
        Fig.\ref{build} shows an example of a build description.
        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
        In Fig.\ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
        {\it C\_EXP} calls macros defined in C files.

\begin{figure}[t]
\centering
\begin{lstlisting}
cell tMotor Motor {
    port = C_EXP("PORT_A");
};
cell tCaller Caller {
    cMotor = Motor.eMotor;
};
\end{lstlisting}
\caption{Build Description}
\label{build}
\end{figure}

@@

\subsection{Development Flow}

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/TECSFlow.pdf}
    \caption{Development flow using TECS}
    \label{fig:TECSFlow}
\end{figure}

@@

\section{mruby}
\label{sec:mruby}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mruby.pdf}
    \caption{mruby/RiteVM mechanism}
    \label{fig:mruby}
\end{figure}

\section{mruby on TECS}
\label{sec:mrubyonTECS}

@@

\subsection{System Model of mruby on TECS}
% The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyonTECS}.
Each mruby program, which is a bytecode, runs on own RiteVM as a componentized task of an RTOS.
TECS components support various embedded drivers such as motor and sensor drivers.
An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.

@@

\subsection{mruby-TECS Bridge}
There is a significant difference between the execution times of mruby and C language codes.
According to  \cite{par:mrubyonTECS}, mruby programs are several hundred times slower than C programs and the execution of an mruby bytecode on a RiteVM is not as efficient as that of C code.
Thus, it is difficult to use mruby exclusively.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/mrubyTECSbridge.pdf}
\caption{mruby-TECS bridge}
\label{fig:mrubyTECSbridge}
\end{figure}

@@

%3
\chapter{Proposed Framework}
\label{sec:Proposed Framework}

@@

\section{TINET+TECS}
\label{sec:TINET+TECS}

\subsection{TINET}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/TINETHierarchyDiagram.pdf}
    \caption{TINET and TOPPERS/ASP3 hierarchy diagrams}
    \label{fig:TINETHierarchyDiagram}
\end{figure}

\subsection{Component Design of TINET+TECS}

@@

\subsection*{Components of a protocol stack}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/ComponentProtocolStack.pdf}
    \caption{Component diagram of a protocol stack}
    \label{fig:ComponentProtocolStack}
\end{figure}

@@

\subsection*{Memory allocator component}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/tMemoryAllocator.pdf}
    \caption{Component diagram of tMemoryAllocator}
    \label{fig:tMemoryAllocator}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/SendReceive.pdf}
    \caption{Differences between in/out and send/receive}
    \label{fig:SendReceive}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sNicDriver {
  void start(
    [send(sNetworkAlloc),size_is(size)]
        int8_t *outputp, .., ..);
  void read(
    [receive(sNetworkAlloc),size_is(*size)]
        int8_t **inputp, .., ..);
    /* Omit: other functions */
};
\end{lstlisting}
\caption{Signature description of the nic driver (An example of send/receive)}
\label{src:SendReceive}
\end{figure}

\subsection{Dynamic connection in TECS}
\label{sec:DynamicConnection}

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/DynamicConnection.pdf}
    \caption{Dynamic connection}
    \label{fig:DynamicConnection}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.0cm,clip]{figure/DynamicConnectionUseCase.pdf}
    \caption{Dynamic connection between CEP and REP}
    \label{fig:DynamicConnectionUseCase}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sRepSelector {
    void  getRep([out]Descriptor(sREP4) *desc,
                 [in]int_t i);
};
celltype tRepSelector {
    entry sRepSelector eRepSelector;
    [ref_desc]
        call sREP4 cREP[NUM_REP];
};
celltype tTCPCEP {
    call sRepSelector cRepSelector;
    [dynamic]
        call sREP4 cREP;
    /* Omit: other call/entry ports */
    /* Omit: attributes and variables */
};
\end{lstlisting}
\caption{Signature and celltype description for the dynamic connection}
\label{src:DynamicCDLcode}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
eAPI_accept (.., ..) {
    /* Get a descriptor of intended REP cell */
    cRepSelector_getRep(&desc, repid);
    /* Set the descriptor */
    cREP_set_descriptor(desc);
    /* Call the function of intended REP cell */
    cREP_getEndpoint();
}
\end{lstlisting}
\caption{Accept function (a dynamic connection example)}
\label{src:DynamicCcode}
\end{figure}

\section{TLSF+TECS}
\label{sec:TLSF+TECS}

\subsection{TLSF}

@@

\subsection{TLSF Algorithms}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/TLSF.pdf}
    \caption{TLSF Algorithm}
    \label{fig:TLSF}
\end{figure}

\subsection{Component Design of TLSF+TECS}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
signature sMalloc {
  int    initializeMemoryPool(void);
  void   *calloc([in]size_t nelem,[in]size_t size);
  void   *malloc([in]size_t size);
  void   *realloc([in]const void *ptr,[in]size_t size);
  void   free([in]const void *ptr);
};
\end{lstlisting}
\caption{Signature description of memory management}  
\label{src:TLSFSignature}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tTLSFMalloc {
    [inline]entry  sMalloc  eMalloc;
    attr {
        size_t  memoryPoolSize;
    };
    var {
        [size_is(memoryPoolSize/8)]uint64_t *pool;
    };
};
\end{lstlisting}
\caption{Celltype description of TLSF memory allocator component}  
\label{src:TLSFCelltype}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/WithoutTECS.pdf}
    \caption{TLSF before componentization}
    \label{fig:WithoutTECS}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/WithTECS.pdf}
    \caption{TLSF after componentization}
    \label{fig:WithTECS}
\end{figure}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}
cell tTask Task_001 {
    cMalloc = TLSFMalloc_001.eMalloc;
};
cell tTLSFMalloc TLSFMalloc_001 {
    memoryPoolSize = 1024*1024; /* 1MB */
};
cell tTask Task_002 {
    cMalloc = TLSFMalloc_002.eMalloc;
};
cell tTLSFMalloc TLSFMalloc_002 {
    memoryPoolSize = 2*1024*1024; /* 2MB */
};
\end{lstlisting}
\caption{Build description of TLSF memory allocator component}
\label{src:TLSFBuild}
\end{figure}

\begin{figure}[t]
\centering
\begin{lstlisting}
void*
mrb_TECS_allocf(mrb_state *mrb, void *p, 
                  size_t size, void *ud)
{
    CELLCB	*p_cellcb = (CELLCB *)ud;
    if (size == 0) {
        //tlsf_free(p);
        cMalloc_free(p);
        return NULL;
    }
    else if (p) {
        //return tlsf_realloc(p, size);
        return cMalloc_realloc(p, size);
    }
    else {
        //return tlsf_malloc(size);
        return cMalloc_malloc(size);
    }
}
\end{lstlisting}
\caption{Example of TLSF memory allocator component}  
\label{src:TLSFC}
\end{figure}

@@

\subsection*{Multiple RiteVM}

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/UseCase_mruby.pdf}
    \caption{Component description of RiteVM and TLSF+TECS}
    \label{fig:UseCase_mruby}
\end{figure}

@@

\subsection*{Memory management for data sending and receiving}

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/UseCase_TINET.pdf}
    \caption{Fixed-size and TLSF memory allocator components}
    \label{fig:UseCase_TINET}
\end{figure}

@@

\section{Use case}
\label{sec:UseCase}

@@

\begin{figure}[t]
\centering
\begin{lstlisting}[language=Ruby]
begin
    io = AnalogIO.new(A0, INPUT)
    cep = TCP.new()	
    cep.accept
    loop do		
        val = io.read  
        cep.snd val.to_s + "\n"		
        RTOS.delay(1000)			
    end
rescue => e	
    puts "[ERROR]" + e
end
\end{lstlisting}
\caption{Example of mruby application}
\label{src:mruby}
\end{figure}

\chapter{Evaluation}
\label{sec:Evaluation}

This chapter describes the experimental evaluation used to demonstrate the effectiveness of the proposed framework.
GR-PEACH was employed as the evaluation board.
Detailed specifications of the board are shown in Table \ref{tab:EvaluationBoardEnvironment}.
We also employ TINET 1.5.4 and the compiler arm-none-eabi-gcc 5.2
To pretest the system, we connected the board to a host PC via a LAN cable and evaluated the data sending and receiving.

\begin{table}[t]
    \centering
    \caption{Evaluation Board Environment}
    \begin{tabular}{l|l}
        \hline\hline
        Board           &   GR-PEACH                \\
        CPU             &   Cortex-A9 RZ/A1H 400MHz \\
        Flash ROM       &   8 MB                    \\
        RAM             &   10 MB                   \\
        LAN Controller  &   LAN8710A                \\
        \hline
    \end{tabular}
    \label{tab:EvaluationBoardEnvironment}
\end{table}

\section{Performance of TINET+TECS}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/EvaluationOfExecutionTime.pdf}
    \caption{Execution times of TINET and TINET+TECS}
    \label{fig:EvaluationOfExecutionTime}
\end{figure}

@@

%5
\chapter{Related Work}
\label{sec:Related Work}

@@

%6
\chapter{Conclusion}
\label{sec:Conclusion}
